\chapter{Manual Testing}
\label{app:manual-testing}
\begin{longtable}{|c|p{6cm}|p{4cm}|c|}
\caption{Manual Test Cases for VitalMonitor Web Dashboard} \label{tab:manual_tests_web} \\
\hline
\textbf{Test Case ID} & \textbf{Test Details} & \textbf{Expected Results} & \textbf{Pass/Fail} \\
\hline
\endfirsthead

\multicolumn{4}{c}%
{{\bfseries Table \thetable\ Continued from previous page}} \\
\hline
\textbf{Test Case ID} & \textbf{Test Details} & \textbf{Expected Results} & \textbf{Pass/Fail} \\
\hline
\endhead

\hline
\multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot

\hline
\endlastfoot

TC-WD01 & Verify that admins can register an organization using valid details. \newline
- Navigate to registration form. \newline
- Input all required fields. \newline
- Submit form. & Admins are taken to home page. & Pass\\
\hline
TC-WD02 & Verify admin login functionality with correct credentials. \newline
- Access login page. \newline
- Enter valid credentials. \newline
- Click login. & Admin is redirected to the dashboard home page. & Pass \\
\hline
TC-WD03 & Verify the addition of a new device. \newline
- Log in as admin. \newline
- Navigate to "Add New Device" page. \newline
- Enter device details and submit. & Device addition confirmation message is displayed. & Pass \\
\hline
TC-WD04 & Verify user-device assignment functionalities. \newline
- Log in and view user list. \newline
- Select a user without a device. \newline
- Assign a device and submit. & Device is listed as assigned to the user. & Pass \\
\hline
TC-WD05 & Check the functionality of logging out. \newline
- Log in to the dashboard. \newline
- Click the logout button. & User is redirected to the login screen and session ends. & Pass \\
\hline
\end{longtable}

\begin{longtable}{|c|p{6cm}|p{4cm}|c|}
\caption{Manual Test Cases for Smart Patch Device} \label{tab:manual_tests_device} \\
\hline
\textbf{Test Case ID} & \textbf{Test Details} & \textbf{Expected Results} & \textbf{Pass/Fail} \\
\hline
\endfirsthead

\multicolumn{4}{c}%
{{\bfseries Table \thetable\ Continued from previous page}} \\
\hline
\textbf{Test Case ID} & \textbf{Test Details} & \textbf{Expected Results} & \textbf{Pass/Fail} \\
\hline
\endhead

\hline
\multicolumn{4}{|r|}{{Continued on next page}} \\ \hline
\endfoot

\hline
\endlastfoot

TC-SP01 & Verify activation of the Smart Patch by pressing the button. \newline
- Ensure the device is off. \newline
- Press the activation button. & Device turns on (red light indicator) and starts transmitting data. & Pass \\
\hline
TC-SP02 & Verify deactivation of Smart Patch by pressing the button again. \newline
- Ensure the device is on. \newline
- Press the button again. & Device turns off (red light off) and stops transmitting data. & Pass \\
\hline
TC-SP03 & Verify continuous data transmission of heart rate and temperature. \newline
- Activate the device. \newline
- Monitor the data transmission for 10 minutes. & Continuous, accurate data transmission is observed. & Pass \\
\hline
\end{longtable}